Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-05 p2/axioms.tex
Fixed typos

\begin{mydef}[$\equiv$]
% Relation in the algebra
$A\equiv B$,
or $A$ and $B$ are \emph{equivalent,}
iff $A\eqext B$ and $B\eqext A$;
that is, $\equiv$ is the intersection of the preorder $\equext$ with its inverse,
and so it is a congruence.
% symmetric: aRb <=> bRa
% reflexive: aRa
% transitive: aRb & bRC => aRc
% old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
\end{mydef}

@@

\begin{mylem}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we assume that $A\equext B$ and $B\equext A$.
$B\equext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
\end{proof}

>>>>

\begin{mydef}[$\equiv$]
% Relation in the algebra
$A\equiv B$,
or $A$ and $B$ are \emph{equivalent,}
iff $A\eqext B$ and $B\eqext A$;
that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
and so it is a congruence.
% symmetric: aRb <=> bRa
% reflexive: aRa
% transitive: aRb & bRC => aRc
% old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
\end{mydef}

@@

\begin{mylem}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we assume that $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
\end{proof}
